ElegantNote：一个优美的 \LaTeX{} 笔记模板

### 2021-09-13 note-temp/elegantnote-cn.tex
Update

%%%%%%%%%%%%%%%%%%%%%%%%% Code Style %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Matlab highlight color settings
%\definecolor{mBasic}{RGB}{248,248,242}       % default
\definecolor{mKeyword}{RGB}{0,0,255}          % bule
\definecolor{mString}{RGB}{160,32,240}        % purple
\definecolor{mComment}{RGB}{34,139,34}        % green
\definecolor{mBackground}{RGB}{245,245,245}   % lightgrey
\definecolor{mNumber}{RGB}{128,128,128}       % gray

\lstset{language=matlab,               % choose the language of the code
  xleftmargin=20pt,
  xrightmargin=20pt,
  frame=tlbr,framesep=6pt,framerule=0.5pt, % sets the frame style
  %frame=shadowbox,rulesepcolor=\color{red!20!green!20!blue!20},
  basicstyle=\footnotesize\ttfamily,
  keywordstyle={\color{mKeyword}},     % sets color for keywords
  stringstyle={\color{mString}},       % sets color for strings
  commentstyle={\color{mComment}},     % sets color for comments
  backgroundcolor=\color{gray!5},      %\color{pBackground}, % choose the background color
  rulecolor=\color{gray!50},
  %title=\lstname,                      % \lstname show the filename of files
  keywords={break,case,catch,classdef,continue,else,elseif,end,for,
  function,global,if,otherwise,parfor,persistent,return,spmd,switch,try,while},
  showspaces=false,                    % show spaces adding particular underscores
  showstringspaces=false,              % underline spaces within strings
  showtabs=false,                      % show tabs within strings adding particular underscores
  tabsize=4,                           % sets default tabsize to 2 spaces
  captionpos=t,                        % sets the caption-position to bottom
  breaklines=true,                     % sets automatic line breaking
}

%\lstinputpath{./M-files/}
\newcommand*\lstinputpath[1]{\lstset{inputpath=#1}}
\lstinputpath{{./M-files/}}

% Using: \lstinputlisting{Euler1.m}

\lstset{basicstyle=\footnotesize\fontspec{Consolas}}
%\lstset{basicstyle=\footnotesize\fontspec{Courier New}}

%\renewcommand{\lstlistingname}{\texttt{Listing}}%
%
%\newcommand{\mylisting}[2][]{%
%    \lstinputlisting[style=MyStyle,caption=\texttt{\detokenize{#2}},#1]{#2}%
%}

%\usepackage[numbered,autolinebreaks,useliterate]{mcode} % framed,
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{MATLAB代码}

\begin{lstlisting}
% Euler1.m
% Euler method for the ODE model
% u'(t)=t^2+t-u, t \in [0,1]
% Initial condition : u(0)=0 ;
% Exact solution : u(t)=-exp(-t)+t^2-t+1.
clear all
h=0.1;
x=0:h:1;                       % function interval
n=length(x)-1;
u(1)=0;                        % initial value
fun=@(t,u) t.^2+t-u;           % RHS
for i=1:n
    u(i+1)=u(i)+h.*fun(x(i),u(i));
end
ue=-exp(-x)+x.^2-x+1;          % exact solution
plot(x,ue,'b-',x,u,'r+','LineWidth',1.5)
xlabel('x','fontsize', 16), ylabel('y','fontsize',16,'Rotation',0)
legend('Exact ','Numerical','location','North')
title('Euler Method','fontsize',14)
set(gca,'fontsize',14)
\end{lstlisting}

>>>>

%\usepackage{fancyhdr}
%\fancyhf{}
%\cfoot{\thepage}

@@
